Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-25 Documents/FP in NAGs/neurips_2021.tex
various edits

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as in
  Def.~\ref{def::NE}. Then we show that the Fictitious Play
  dynamic on the NA game admits solutions. Finally, we show that NA-CTFP reaches a fixed point when
  the NA game is zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them to the
  supplementary material (Sections (S4 - S6)).

  As a reminder, the NE condition (Def. \ref{def::NE}) states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

@@

  With these in place, we can build towards our main result, namely that of convergence of NA-CTFP to an NE. In order to do this, we first need to establish that the NE, and an NA-CTFP (i.e. a path which satisfies Def.~\ref{def::NACTFP}) exists.

@@

  \begin{theorem}
    There exists a path $m$ which satisfies the property that, for all agents $\mu$, $m^\mu \in
    BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
  \end{theorem}

With these results in place, we can show that NA-CTFP converges
to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
all limit points for $\alpha(t)$. Then, a NA-CTFP path is said to have
converged if $\Omega(\alpha)$ is contained within the set of Nash
Equilibria of the game. We adapt the techniques
of \cite{Ewerhart2020} to prove that this is the case.
%
  \begin{theorem} \label{thm::NACTFPtoFixed}
    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, $\alpha(t; m)$ (i.e. the time-averaged state) converges to a set of fixed points.
  \end{theorem}

  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality yields that, for all $\mu$
%
  \begin{equation} 
    u^\mu(y, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq u^\mu(\xmu_\infty, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty)
  \end{equation}

>>>>

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as defined in
  Def.~\ref{def::NE}. Then we show that the Fictitious Play
  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?}. Finally, we show that NA-CTFP reaches a fixed point when
  the NA game is zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them, to the
  supplementary material (Sections (S4 - S6)).

  As a reminder,
  %the NE condition (
  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

  \fb{why symbol $=:$? is it a definition?}

@@

  With these in place, we can build towards our main result, namely
  the convergence of NA-CTFP to an NE. In order to do this, we first
  need to establish that the NE, and an NA-CTFP (i.e. a path which
  satisfies Def.~\ref{def::NACTFP}) exists.

@@

  \begin{theorem}
    There exists a path $m$ which satisfies the property that, for all agents $\mu$, $m^\mu \in
    BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
    \fb{why parameter $t$ if it does not appear anywhere in the statement?}
  \end{theorem}

With these results in place, we can show that NA-CTFP converges
to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
all limit points for $\alpha(t)$. Then, a NA-CTFP path is said to {\em 
converge} if $\Omega(\alpha)$ is contained within the set of Nash
Equilibria of the game. We adapt the techniques
of \cite{Ewerhart2020} to prove that this is the case.
%
  \begin{theorem} \label{thm::NACTFPtoFixed}
    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, $\alpha(t; m)$ (i.e. the time-averaged state) converges to a set of fixed points.
  \end{theorem}

  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality \fb{which inequality?} yields that, for all agents $\mu$,
%
  \begin{equation} 
    u^\mu(y, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq u^\mu(\xmu_\infty, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty)
  \end{equation}
